Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-11 manuscript.Rmd
Testing download of processed participant data

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

>>>>

processdata <- 2  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)
